%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% Primordial Machine's Errors Library
% Copyright (C) 2017-2019 Michael Heilmann
%
% This software is provided 'as-is', without any express or implied warranty.
% In no event will the authors be held liable for any damages arising from the
% use of this software.
%
% Permission is granted to anyone to use this software for any purpose,
% including commercial applications, and to alter it and redistribute it
% freely, subject to the following restrictions:
%
% 1. The origin of this software must not be misrepresented;
%    you must not claim that you wrote the original software.
%    If you use this software in a product, an acknowledgment
%    in the product documentation would be appreciated but is not required.
%
% 2. Altered source versions must be plainly marked as such,
%    and must not be misrepresented as being the original software.
%
% 3. This notice may not be removed or altered from any source distribution.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[oneside]{book}

\input{common}
\usepackage{listings}

\SetOrganization{Primordial Machine's}
\SetLibraryName{Errors Library}

\SetLibraryIncludeFileName{include.hpp}
\SetLibraryIncludesDirectoryPath{primordialmachine/errors/\newline\$(PlatformTarget.toLower())/\$(Configuration.toLower())/includes}

\SetLibraryIncludeDirectiveFilePath{primordialmachine/errors/include.hpp}

\SetLibraryVersion{v1.3}
\SetLibraryRepository{https://github.com/primordialmachine/errors}
\SetAuthor{Michael Heilmann}
\SetEmail{michaelheilmann@primordialmachine.com}

\SetDocumentType{User Manual}

\begin{document}
\lstset{language=C++,
  basicstyle=\footnotesize, % reduce the font size.
  showstringspaces=false    % do not display "squat-u" for whitespace.
}

\frontmatter

\begin{titlepage}
\maketitle
\end{titlepage}

\tableofcontents
\addtocontents{toc}{\protect\thispagestyle{empty}}
\pagenumbering{gobble}

\mainmatter

\chapter{Synopsis}
C++ 17 library providing extendable error objects and exceptions.
The library is made available publicly on
\href{\GetLibraryRepository}{Github}
under the
\href{\GetLibraryRepository/blob/master/LICENSE}{MIT License}.

\chapter{Limitations and Restrictions}
The library officially only supports Visual Studio 2017 and Windows 10.

\chapter{Usage example}
The folder \href{\GetLibraryRepository/blob/master/example}{example} contains example programs.

\input{building_visual_studio_2017}

\chapter{Library Interface Documentation}

\section{\texttt{primordialmachine}}
The namespace this library is adding its declarations/definitions to.
The added namespace elements are documented below

\section{\texttt{PRIMORDIALMACHINE\_ERROR\_LOCATION}}
A macro evaluating to an \texttt{error\_location} object with the file name and line number of the
location within the C++ program at which the macro was evaluated.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{\texttt{error\_position}}
Objects of type \texttt{error\_position} represent locations in a C++ program in terms of the   name
of a source file and the line number of a line in that source file. \texttt{error\_position}      is
nothrow (copy|move) (constructible|assignable).

\section{\texttt{constexpr error\_position(const char *file, int line)}}
Construct this \texttt{error\_position} object.
\begin{enumerate}
   \item\texttt{file} is a pointer to a static constant string denoting the name of the C++ source file.
   \item\texttt{line} is a non-negative \texttt{int} value denoting the line in the C++ source file.
\end{enumerate}

\subsection{\texttt{constexpr const char *file() const}}
A pointer to a static constant string denoting the name of the C++ source file.

\subsection{\texttt{constexpr int line() const}}
A positive \texttt{int} value denoting the line in the C++ source file.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{\texttt{error}}
The base class from which to derive custom error types.

\subsection{\texttt{using message\_type} (v1.0)}
An alias for \texttt{std::string}.

\subsection{\texttt{using position\_type} (v1.0)}
An alias for \texttt{primordialmachine::error\_position}.

\subsection{\texttt{error(message\_type message, position\_type position)}}
Construct this error object.
\begin{enumerate}
	\item\texttt{message}: The message of the error.
	\item\texttt{position}: The position associated with the error.
\end{enumerate}

\subsection{\texttt{constexpr message\_type\& message() const}}
Get the message of the error.

\subsection{\texttt{constexpr position\_type\& position() const}}
Get the position of the error.

\subsection{\texttt{void raise() const}}
Raise an \texttt{exception} object wrapping a clone of this \texttt{error} object.

\subsection{\texttt{virtual void raise\_implementation() const} (v1.3)}
May be overriden by any descendant class \texttt{D} of \texttt{error} to raise an
\texttt{exception} or derived type object.
Exceptions raised by this function are propagated.

\subsection{\texttt{virtual error *clone\_implementation() const}}
Must be overriden by any descendant class \texttt{error} to return a clone of the type of that descendant class.
Exceptions raised by this function are propagated.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{\texttt{class exception}}
Class derived from \texttt{std::exception} wrapping around an \texttt{error} or derived type
object. \texttt{exception} or derived types must be nothrow (copy/move) (assignable/constructible).

\subsection{\texttt{using error\_type} (v1.0)}
An alias for \lstinline{primordialmachine::error}.

\subsection{\texttt{error\_exception(const error\_type\& error)}}
Construct this \texttt{error\_exception} object wrapping a clone of the \texttt{error\_type} or
derived type object \texttt{error}.

\subsection{\texttt{constexpr const std\_shared\_ptr\textless{}error\_type\textgreater{}\& error() const}}
Get the wrapped \texttt{error} or derived type object.

\subsection{\texttt{const char *what() const override}}
Override of function in \texttt{std::exception}.
Returns a pointer to the message of the wrapped \texttt{error} or derived type object.

\end{document}
